---
title: "Week 2 Assignment – SQL and R"
author: "Karim Hammoud"
date: "`r Sys.Date()`"
output:
   openintro::lab_report: default

---

## The Overview:

The goal of this assignment is to create and analyze a survey of six movies and add the data to SQL database where we implement the data from a secure password host to the R markdown. the finding of this report is analyzing the movies and find out which one has the most rating.


I conducted the survey by asking friends and coworkers about the six movies, some of them have seen most of the movies and some saw only few of the movies.

I uploaded the files the Github and you can find the [data here](https://github.com/akarimhammoud/607-Data-Acquisition-and-Management-CUNY-SPS-Fall2020/blob/master/Week%202%20R%20and%20SQL/Data/Week%202%20movie_data.csv)

And you can check the files on [Github](https://github.com/akarimhammoud/607-Data-Acquisition-and-Management-CUNY-SPS-Fall2020/tree/master/Week%202%20R%20and%20SQL)

And the [Rpubs](https://rpubs.com/karim7mod/658836)

## Loading packages

```{r load-packages, message=FALSE}
library(RMySQL)
library(ggplot2)
library(dplyr)
```

## getting the row data for csv files saved in Github
```{r}
urlA <- "https://raw.githubusercontent.com/akarimhammoud/607-Data-Acquisition-and-Management-CUNY-SPS-Fall2020/master/Week%202%20R%20and%20SQL/Data/Week%202%20movie_data.csv"

urlB <- "https://raw.githubusercontent.com/akarimhammoud/607-Data-Acquisition-and-Management-CUNY-SPS-Fall2020/master/Week%202%20R%20and%20SQL/Data/Week2_people.csv"
 
rating <- read.csv(urlA, header = TRUE, sep = ",")
rating

people <- read.csv(urlB, header = TRUE, sep = ",")
people
```


## Establish Connection

Connect to MySql on Google Cloud host

```{r}
conn <- dbConnect(MySQL(),
                 user="root", password= "dav",
                 dbname="data607", host= "35.188.162.1")
summary(conn)
```


## Creating Tables

Creating table for rating and people on MySql

```{r}
dbWriteTable(conn, 'rating', rating, overwrite = TRUE)
```

Creating table for the people 

```{r}
dbWriteTable(conn, 'people', people, overwrite = TRUE)
```

### Check the tables in the database

I will mainly use the movies database

```{r}
dbListTables(conn);
```

## Create join the tables using Query
join the rating and people tables and getting the data

```{r}
data <- dbGetQuery(conn, 'select * from rating 
                  inner join people on rating.ID = people.ID;')
data
```

We get rid of the duplicate columns

```{r}
data <- data[, !duplicated(colnames(data))]
data
```

Calculating the mean average of rating for the movies, and considering there are NA 
```{r}
movies <- subset(data, select = c(Frozen.2, Murder.Mystery, Moana, Joker, The.Big.Kick, Get.out))

movies <- colMeans(movies, na.rm = TRUE, dims = 1)

movies
```



## Display the data on a bar chart

After pulling the average rating for each movie we present the data on the chart

```{r}
par(mar=c(5,2,2,0))

barplot(movies, main="Movies Rating", xlab="Movies", ylim=c(0,6), horiz=FALSE,cex.lab=1 , col= c("lightcyan","mistyrose","beige","yellow","red","green"), names.arg=c("Frozen 2", "MurderMystery", "Moana", "Joker", "The Big Kick", "Get out" ))
```

## Conclusion:

As we see in the barchart, the movies Frozen 2 and Joker got the highest average rating evethough Frozen2 had been watched only by 3 people, while Joker had been watched by all of the people in the rating list. on the other side The Big Sick movie got the worst rating of around only 2 out of 5 and it was watched by 4 people, it seems like they didn't enjoy it a lot.

Thanks,
Karim Hammoud
