---
title: "R Character Manipulation and Date Processing"
author: "Karim Hammoud"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

## The Overview:

#1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Loading the required library

```{r}
library(stringr)
```


### Getting the data from fivethirtyeight github

```{r}
url <- ("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv")

data <- read.csv(url, sep = ",")

head(data)
```

### Getting the majors containing "DATA" 

```{r}
data$Major[grepl("DATA", data$Major)]
```

### Getting the majors containing "DATA" 

```{r}
data$Major[grepl("STATISTICS", data$Major)]
```


## 2 Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")


```{r}
fruits <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'

fruits
```
Here we use the str extract for all of the fruits then we join them with comma separator

```{r warning = FALSE}
fruits_string <- str_extract_all(fruits,pattern = '[A-Za-z]+.?[A-Za-z]+')

fruits <- writeLines(str_c(fruits_string, collapse =", "))
```


The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

## 3 Describe, in words, what these expressions will match:

**(.)\1\1**
This is to get one character with two repetitions like "AAA".

**"(.)(.)\\2\\1"**
This is to get two characters repeated in a reverse way like "ABBA" 

**(..)\1**
This is to get two characters repeated like "ABAB"

**"(.).\\1.\\1"**
This is to get 5 characters and three of them are the same like "ABACA"

**"(.)(.)(.).*\\3\\2\\1"**
This is to get a number of characters begin and end with the same characters in a reverse way like "ABC42342CBA"



## 4 Construct regular expressions to match words that:

* Start and end with the same character.
The answer: "(.).*\1"

```{r}
data <- c("church", "individual", "phillip")
str_view(data, "^(.).*\\1$", match = TRUE)
```


* Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
The answer: "(..).*\\1"

```{r}
data <- c("church", "individual", "phillip")
str_view(data, "^(..).*\\1$", match = TRUE)
```


* Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
The answer: "(.).*\\1.*\\1"

```{r}
data <- c("church", "individual", "phillip")
str_view(data, "(.).*\\1.*\\1", match = TRUE)
```
...